---
title: "Grey Matter Risk Score (GMRS)"
author: "Baptiste CRINIERE-BOIZET"
date: "22/07/2021"
output: html_document
---


---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This code concerns the construction of grey matter risk scores as well as their evaluation.
We built our model from a training sample composed of an MRI image of the UK biobank, then we tested our model in a test sample of the UK biobank independent of the training one as well as in another base ADNI data.
# Library
```{r eval=FALSE}
library(tidyverse)
library(LDheatmap)
library(rmarkdown)    
library(epuRate)      
library(vroom)        
library(rrBLUP)
library(stats)
library(matlib)
library(pROC)
library(DescTools)
library(lmtest)
library(FSA)
library(base)
```

# Phenotype & Covariates
## Phenotype
```{r eval=FALSE}
data <- read.table("ukb42624_UKbiobank_BCBinternship_24082020.tab", sep ="\t", header = T)

# We only select individuals who have had a MRI
data <- data[!is.na(data$f.54.2.0),]
# make sure the date is indeed a date
data$f.53.0.0 <- as.Date(data$f.53.0.0)


# Extract the year and convert to numeric format
data$year <- as.numeric(format(data$f.53.0.0, "%Y"))
# Create an age feature
data$age <- data$year - data$f.34.0.0

# We rename the sex feature :
data <- data %>% rename(Sex = f.31.0.0)

# We create the Alzheimer status of the father and the mother
# alz_f : AD father status & alz_M : AD mother status
data$alz_F <- ifelse(data$f.20107.2.0 == 10 | data$f.20107.2.1 == 10 |data$f.20107.2.2 == 10 |data$f.20107.2.3 == 10 |data$f.20107.2.4 == 10 |data$f.20107.2.5 == 10 |data$f.20107.2.6 == 10 |
data$f.20107.2.7 == 10 |data$f.20107.2.8 == 10 |data$f.20107.2.9 == 10, 1, 0)
data$alz_M <- ifelse(data$f.20110.2.0 == 10 | data$f.20110.2.1 == 10  | data$f.20110.2.2 == 10 | data$f.20110.2.3 == 10 |data$f.20110.2.4 == 10 |data$f.20110.2.5 == 10 |data$f.20110.2.6 == 10 |
data$f.20110.2.7 == 10 |data$f.20110.2.8 == 10 |data$f.20110.2.9 == 10 |data$f.20110.2.10 == 10, 1, 0)
data$alz_F <- ifelse(is.na(data$alz_F), 0, 1)
data$alz_M <- ifelse(is.na(data$alz_M), 0, 1)

# On compte le nombre de valeur manquante :
sum(is.na(data$f.1845.0.0))
sum(is.na(data$f.2946.0.0))
data[data$alz_F==1 & data$alz_M==1,]
# Prévalence de la maladie :
table(data$alz_F)
table(data$alz_M)

#We deal with missig value
#Mother age of death at imaging
data$f.3526.0.0 <- ifelse(is.na(data$f.3526.0.0), 0, data$f.3526.0.0)
data$f.3526.1.0 <- ifelse(is.na(data$f.3526.1.0), 0, data$f.3526.1.0)
data$f.3526.2.0 <- ifelse(is.na(data$f.3526.2.0), 0, data$f.3526.2.0)
#Mother age at imaging
data$f.1845.0.0 <- ifelse(is.na(data$f.1845.0.0), 0, data$f.1845.0.0)
data$f.1845.1.0 <- ifelse(is.na(data$f.1845.1.0), 0, data$f.1845.1.0)
data$f.1845.2.0 <- ifelse(is.na(data$f.1845.2.0), 0, data$f.1845.2.0)

absmax <- function(x, na.rm = FALSE) {max(abs(x), na.rm = na.rm)}
# On fait une boucle
for (i in 1:nrow(data)){
  data$age_M_A[i] <- ifelse(data$f.1845.0.0[i]<=0, absmax(c(data$f.1845.0.0[i], data$f.1845.1.0[i], data$f.1845.2.0[i])), data$f.1845.0.0[i])
}
for (i in 1:nrow(data)){
  data$age_M_D[i] <- ifelse(data$f.3526.0.0[i]<=0, absmax(c(data$f.3526.0.0[i], data$f.3526.1.0[i], data$f.3526.2.0[i])), data$f.3526.0.0[i])
}
for (i in 1:nrow(data)){
  data$age_Mother[i] <- data$age_M_A[i]
  if (data$age_M_A[i] <= 3){
    data$age_Mother[i] <- data$age_M_D[i]
  }
}


#We deal with missing value
#Father age of death at imaging
data$f.2946.0.0 <- ifelse(is.na(data$f.2946.0.0), 0, data$f.2946.0.0)
data$f.2946.1.0 <- ifelse(is.na(data$f.2946.1.0), 0, data$f.2946.1.0)
data$f.2946.2.0 <- ifelse(is.na(data$f.2946.2.0), 0, data$f.2946.2.0)
#Father age at imaging
data$f.1807.0.0 <- ifelse(is.na(data$f.1807.0.0), 0, data$f.1807.0.0)
data$f.1807.1.0 <- ifelse(is.na(data$f.1807.1.0), 0, data$f.1807.1.0)
data$f.1807.2.0 <- ifelse(is.na(data$f.1807.2.0), 0, data$f.1807.2.0)

#We do a loop
for (i in 1:nrow(data)){
  data$age_F_A[i] <- ifelse(data$f.1807.0.0[i]<=0, absmax(c(data$f.1807.0.0[i], data$f.1807.1.0[i], data$f.1807.2.0[i])), data$f.1807.0.0[i])
}
for (i in 1:nrow(data)){
  data$age_F_D[i] <- ifelse(data$f.2946.0.0[i]<=0, absmax(c(data$f.2946.0.0[i], data$f.2946.1.0[i], data$f.2946.2.0[i])), data$f.2946.0.0[i])
}
for (i in 1:nrow(data)){
  data$age_Father[i] <- data$age_F_A[i]
  if (data$age_F_A[i] <= 3){
    data$age_Father[i] <- data$age_F_D[i]
  }
}

#We create the phenotype father and mother
phenotype <- data %>% select(f.eid, alz_F, age_Father, alz_M, age_Mother)
phenotype_father <- phenotype %>% select(f.eid, alz_F, age_Father)
phenotype_father <- phenotype_father[phenotype_father$age_Father>=65,]
phenotype_father <- phenotype_father %>% select(f.eid, alz_F)
phenotype_mother <- phenotype %>% select(f.eid, alz_M, age_Mother)
phenotype_mother <- phenotype_mother[phenotype_mother$age_Mother>=65,]
phenotype_mother <- phenotype_mother %>% select(f.eid, alz_M)
phenotype_father$id <- phenotype_father$f.eid
phenotype_father <- phenotype_father %>% select(id, f.eid, alz_F) 
phenotype_mother$id <- phenotype_mother$f.eid
phenotype_mother <- phenotype_mother %>% select(id, f.eid, alz_M) 
write.table(phenotype_father, "phenotype_father.txt", col.names = F, row.names = F, quote=F)
write.table(phenotype_mother, "phenotype_mother.txt", col.names = F, row.names = F, quote=F)
#We create the proxy phenotype
proxy_phenotype <- phenotype
for (i in 1:nrow(proxy_phenotype)){
proxy_phenotype$proxy_Father[i] <- ifelse(proxy_phenotype$alz_F[i]==1, proxy_phenotype$alz_F[i], min(abs(max(1-proxy_phenotype$age_Father[i]/100, 0)), 0.32))
proxy_phenotype$proxy_Mother[i] <- ifelse(proxy_phenotype$alz_M[i]==1, proxy_phenotype$alz_M[i], min(abs(max(1-proxy_phenotype$age_Mother[i]/100, 0)), 0.32))}
proxy_phenotype$id <- proxy_phenotype$f.eid
proxy_phenotype$proxy <- proxy_phenotype$proxy_Mother + proxy_phenotype$proxy_Father
proxy_phenotype <- proxy_phenotype %>% select(f.eid, proxy)
write.table(proxy_phenotype, "phenotype_proxy.txt", col.names = F, row.names = F, quote=F)
```
## Covariates
```{r eval=FALSE}
# Covariables : age, sex, Volumetric scaling from T1 head image to standard space :
covariates <- data %>% select(f.eid, age, f.25000.2.0)
covariates$id <- covariates$f.eid
covariates <- covariates %>% select(id, f.eid, age, f.25000.2.0)
write.table(covariates, "covariates.txt", col.names = F, row.names = F, quote=F)
```

# Data Management
## Variance filter
We select the voxels which have a variance greater than a certain threshold, here we have chosen a threshold of 0.2
```{r eval=FALSE}
osca --befile data --sd-min 0.2 --make-bod --out filtered_data
```
## Recover the name of voxels
We recover the names of the Voxels that we selected with the exclusion criterion.
```{r eval=FALSE}
fls <- read.table("filtered_data.opi", stringsAsFactors = F)
fls <- fls %>% select(V2)
write.table(fls, "Voxel_selection.tsv", col.names = F, row.names = F, quote= F)
```
# Calculation of the ORM
## By making a loop
### ORM division
We divide the calculation of the ORM into 10, because it is very heavy to do in one.
```{r eval=FALSE}
fls <- read.table("filtered_data.opi", stringsAsFactors = F)
fls <- fls %>% select(V2)
d <- split(fls, (seq(nrow(fls))-1) %/% 15000)
for (i in 1:length(d)) {
  write.table(as.data.frame(d[i]), paste0("Vox_", i), col.names = F, row.names = F, quote=F)
}
```
### ORM Loop
We make a loop to calculate the ORM
```{bash eval=FALSE}
for nb in {1..10}; do
osca --befile filtered_data --extract-probe  $wd/Batch/Voxels/Vox_"${nb}" --make-bod --out data_"${nb}"
done
for nb in {1..10}; do
osca --befile filtered_data --extract-probe Vox_"${nb}" --make-orm --out ORM/ORM_"${nb}"
done 
```
### We delete the .id extension
```{r eval=FALSE}
fls <- read.table("ORMs.tsv", stringsAsFactors = F)
fls$V1 <- substr(fls$V1, 1, 83)
write.table(fls, "ORMs.tsv", col.names = F, row.names = F, quote = F)
```
### Merge ORM
```{bash eval=FALSE}
ls -d ORM/*.id > ORM/ORMs.tsv
osca --multi-orm ORM/ORMs.tsv --make-orm --out ORM
```
## ORM calculation directly
```{bash eval=FALSE}
osca --befile filtered_data --make-orm --out ORM
```

# BLUP with AD status of the mother as phenotype
## BLUP 1
```{bash eval=FALSE}
osca --reml --orm ORM --qcovar covariates.txt  --pheno phenotyp_mother.txt --reml-pred-rand --out blup_mother
```
## BLUP 2
```{bash eval=FALSE}
osca --befile filtered_data covariates.txt --blup-probe blup_mother.indi.blp --out myblp_mother
```
## BLUP 3 : SCORE calculation
```{bash eval=FALSE}
osca --befile reprod1 --score myblp_mother.probe.blp --out SCORE_mother_reprod
osca --befile ADNI --score myblp_mother.probe.blp --out SCORE_mother_ADNI 
```
# BLUP with AD status of the father as phenotype
## BLUP 1
```{bash eval=FALSE}
osca --reml --orm ORM --qcovar covariates.txt  --pheno phenotype_father.txt --reml-pred-rand --out blup_father
```
## BLUP 2
```{bash eval=FALSE}
osca --befile filtered_data covariates.txt --blup-probe blup_father.indi.blp --out myblp_father
```
## BLUP 3 : SCORE calculation
```{bash eval=FALSE}
osca --befile reprod1 --score myblp_father.probe.blp --out SCORE_father_reprod
osca --befile ADNI --score myblp_father.probe.blp --out SCORE_father_ADNI 
```
# BLUP with proxy phenotype as phenotype
## BLUP 1
```{bash eval=FALSE}
osca --reml --orm ORM --qcovar covariates.txt  --pheno phenotype_proxy.txt --reml-pred-rand --out blup_proxy
```
## BLUP 2
```{bash eval=FALSE}
osca --befile filtered_data covariates.txt --blup-probe blup_proxy.indi.blp --out myblp_proxy
```
## BLUP 3 : SCORE calculation
```{bash eval=FALSE}
osca --befile reprod --score myblp_proxy.probe.blp --out SCORE_proxy_reprod
osca --befile ADNI --score myblp_proxy.probe.blp --out SCORE_proxy_ADNI 
```

# Results
## UKbiobank reproductibility
### Proxy phenotype
```{r eval=FALSE}
# Scores
ukb <- read.table("SCORE_proxy_reprod.profile", sep ="\t", header = T)
ukb <- ukb %>% select(IID, SCORE)
# Phenotype
proxy_phenotype <- read.table("pheotype_proxy.txt", sep =" ", header = F)
proxy_phenotype <- proxy_phenotype %>% select(V1, V3)
proxy_phenotype <- proxy_phenotype %>% rename(Proxy=V3)
prediction <- merge(ukb, proxy_phenotype, by.x = "IID", by.y = "V1")
# Covariates
covariates <- read.table("covariates.txt", sep =" ", header = F)
covariates <- covariates %>% select(V1, V3, V4, V5)
covariates <- covariates %>% rename(Age=V3,Sex=V4,Volume=V5)
prediction <- merge(prediction, covariates, by.x = "IID", by.y = "V1" )
# Results
a <- lm(formula = Proxy ~ Age + Sex + Volume, data = prediction)
a1 <- summary(a)$r.squared
b <- lm(formula = Proxy ~ SCORE + Age + Sex + Volume, data = prediction)
b1 <- summary(b)$r.squared
b1-a1
summary(b)
```
## Mother phenotype
```{r eval=FALSE}
# Scores
ukb <- read.table("SCORE_mother_reprod.profile", sep ="\t", header = T)
ukb <- ukb %>% select(IID, SCORE)
# Phenotype
mother_phenotype <- read.table("phenotype_mother.txt", sep =" ", header = F)
mother_phenotype <- mother_phenotype %>% select(V1, V3)
mother_phenotype <- mother_phenotype %>% rename(Proxy=V3)
prediction <- merge(ukb, mother_phenotype, by.x = "IID", by.y = "V1")
# Covariates
covariates <- read.table("covariates.txt", sep =" ", header = F)
covariates <- covariates %>% select(V1, V3, V4, V5)
covariates <- covariates %>% rename(Age=V3,Sex=V4,Volume=V5)
prediction <- merge(prediction, covariates, by.x = "IID", by.y = "V1" )
# Results
a <- glm(formula = Proxy ~ Age + Sex + Volume, data = prediction, family = binomial())
a1 <- PseudoR2(a, which = "Efron")
b <- glm(formula = Proxy ~ SCORE + Age + Sex + Volume, data = prediction, family = binomial())
b1 <- PseudoR2(b, which = "Efron")
b1-a1
summary(b)
```

## Father phenotype
```{r eval=FALSE}
# Scores
ukb <- read.table("SCORE_father_reprod.profile", sep ="\t", header = T)
ukb <- ukb %>% select(IID, SCORE)
# Phenotype
father_phenotype <- read.table("phenotype_father.txt", sep =" ", header = F)
father_phenotype <- father_phenotype %>% select(V1, V3)
father_phenotype <- father_phenotype %>% rename(Proxy=V3)
prediction <- merge(ukb, father_phenotype, by.x = "IID", by.y = "V1")
# Covariates
covariates <- read.table("covariates.txt", sep =" ", header = F)
covariates <- covariates %>% select(V1, V3, V4, V5)
covariates <- covariates %>% rename(Age=V3,Sex=V4,Volume=V5)
prediction <- merge(prediction, covariates, by.x = "IID", by.y = "V1" )
# Results
a <- glm(formula = Proxy ~ Age + Sex + Volume, data = prediction, family = binomial())
a1 <- PseudoR2(a, which = "Efron")
b <- glm(formula = Proxy ~ SCORE + Age + Sex + Volume, data = prediction, family = binomial())
b1 <- PseudoR2(b, which = "Efron")
summary(b)
b1-a1
```
## ADNI results
### Proxy phenoype
#### Data management
```{r eval=FALSE}
# ADNI phenotypes
ADNI1 <- vroom(file = 'ADNI1_phenotypes_all_2020Update_conversion.txt')
ADNI2 <- vroom(file = 'ADNI2_GO_phenotypes_all_2020Update_conversion.txt')
ADNI1 <- ADNI1 %>% select(PTID, Alz_bl, AGE, PTGENDER, PTEDUCAT, SITE, AlzProg, CDRSB_bl, ADAS11_bl, ADAS13_bl,MMSE_bl, ABETA_bl, TAU_bl, PTAU_bl, AlzMCI_bl, conversion1year, conversion2year, conversion3year,conversion4year, conversion5year, conversion10year)
ADNI2 <- ADNI2 %>% select(PTID, Alz_bl, AGE, PTGENDER, PTEDUCAT, SITE, AlzProg, CDRSB_bl, MMSE_bl, ABETA_bl, TAU_bl, PTAU_bl, AlzMCI_bl, conversion1year, conversion2year, conversion3year,
conversion4year, conversion5year, conversion10year)
adnibis1 <- vroom(file = 'ADNI1_phenotypes_all.txt')
adnibis1 <- adnibis1 %>% select(PTID, ICV.y)
adnibis2 <- vroom(file = 'ADNI2_GO_phenotypes_all.txt')
adnibis2 <- adnibis2 %>% select(PTID, ICV.y)
adnibis <- rbind(adnibis1, adnibis2)
ADNI <- rbind(ADNI1, ADNI2)
ADNI <- merge(ADNI, adnibis, by.x = "PTID", by.y = "PTID")
# ADNI scores
adni <- read.table("SCORE_proxy_ADNI.profile", sep ="\t", header = T)
adni <- adni %>% select(IID, SCORE)
ADNI$PTID <- paste0(paste0(substr(ADNI$PTID, 1, 3), substr(ADNI$PTID, 5, 5)), substr(ADNI$PTID, 7, 10))
ADNI <- merge(ADNI, adni, by.x = "PTID", by.y = "IID")
```
#### Results
```{r eval=FALSE}
# Phenotype Alzheimer
# We also can test other phenotype by remplacing Alz_bl by conversion1year, Tau_bl, etc.
a <- glm(Alz_bl ~ SCORE + AGE + PTGENDER + ICV.y, data = ADNI, family = binomial())
a1 <- PseudoR2(a, which = "Efron")
b <- glm(Alz_bl ~ ICV.y + AGE + PTGENDER, data = ADNI, family = binomial())
b1 <- PseudoR2(b, which = "Efron")
b1-a1
summary(a)
```
### Mother phenoype
#### Data management
```{r eval=FALSE}
# ADNI phenotypes
ADNI1 <- vroom(file = 'ADNI1_phenotypes_all_2020Update_conversion.txt')
ADNI2 <- vroom(file = 'ADNI2_GO_phenotypes_all_2020Update_conversion.txt')
ADNI1 <- ADNI1 %>% select(PTID, Alz_bl, AGE, PTGENDER, PTEDUCAT, SITE, AlzProg, CDRSB_bl, ADAS11_bl, ADAS13_bl,MMSE_bl, ABETA_bl, TAU_bl, PTAU_bl, AlzMCI_bl, conversion1year, conversion2year, conversion3year,conversion4year, conversion5year, conversion10year)
ADNI2 <- ADNI2 %>% select(PTID, Alz_bl, AGE, PTGENDER, PTEDUCAT, SITE, AlzProg, CDRSB_bl, MMSE_bl, ABETA_bl, TAU_bl, PTAU_bl, AlzMCI_bl, conversion1year, conversion2year, conversion3year,
conversion4year, conversion5year, conversion10year)
adnibis1 <- vroom(file = 'ADNI1_phenotypes_all.txt')
adnibis1 <- adnibis1 %>% select(PTID, ICV.y)
adnibis2 <- vroom(file = 'ADNI2_GO_phenotypes_all.txt')
adnibis2 <- adnibis2 %>% select(PTID, ICV.y)
adnibis <- rbind(adnibis1, adnibis2)
ADNI <- rbind(ADNI1, ADNI2)
ADNI <- merge(ADNI, adnibis, by.x = "PTID", by.y = "PTID")
# ADNI scores
adni <- read.table("SCORE_mother_ADNI.profile", sep ="\t", header = T)
adni <- adni %>% select(IID, SCORE)
ADNI$PTID <- paste0(paste0(substr(ADNI$PTID, 1, 3), substr(ADNI$PTID, 5, 5)), substr(ADNI$PTID, 7, 10))
ADNI <- merge(ADNI, adni, by.x = "PTID", by.y = "IID")
```
#### Results
```{r eval=FALSE}
# Phenotype Alzheimer
# We also can test other phenotype by remplacing Alz_bl by conversion1year, Tau_bl, etc.
a <- glm(Alz_bl ~ SCORE + AGE + PTGENDER + ICV.y, data = ADNI, family = binomial())
a1 <- PseudoR2(a, which = "Efron")
b <- glm(Alz_bl ~ ICV.y + AGE + PTGENDER, data = ADNI, family = binomial())
b1 <- PseudoR2(b, which = "Efron")
b1-a1
summary(a)
```
#### Mother phenotype ADNI
```{r eval=FALSE}
# Parent
A1 <- vroom(file = 'ADNI1_parent.txt')
A1 <- A1 %>% select(PTID, FHQMOM, FHQDAD, FHQDADAD, FHQMOMAD,AGE, PTGENDER)
A2 <- vroom(file = 'ADNI2_parent')
A2 <- A2 %>% select(PTID, FHQMOM, FHQDAD, FHQDADAD, FHQMOMAD,AGE, PTGENDER)
A <- rbind(A1, A2)
adni <- read.table("SCORE_mother_ADNI.profile", sep ="\t", header = T)
adni <- adni %>% select(IID, SCORE)
A$PTID <- paste0(paste0(substr(A$PTID, 1, 3), substr(A$PTID, 5, 5)), substr(A$PTID, 7, 10))
A <- merge(A, adni, by.x = "PTID", by.y = "IID")
A <- merge(A, ADNI, by.x = "PTID", by.y = "PTID")
A <- A %>% filter(FHQMOMAD == 0 | FHQMOMAD == 1)
#Resultats
b <- glm(FHQMOMAD ~ AGE.y + PTGENDER.y + ICV.y, data = A, family = binomial())
b1 <- PseudoR2(b, which = "Efron")
c <- glm(FHQMOMAD ~ SCORE + AGE.y + PTGENDER.y + ICV.y, data = A, family = binomial())
c1 <- PseudoR2(c, which = "Efron")
c1-b1
summary(c)
```
### Father phenoype
#### Data management
```{r eval=FALSE}
# ADNI phenotypes
ADNI1 <- vroom(file = 'ADNI1_phenotypes_all_2020Update_conversion.txt')
ADNI2 <- vroom(file = 'ADNI2_GO_phenotypes_all_2020Update_conversion.txt')
ADNI1 <- ADNI1 %>% select(PTID, Alz_bl, AGE, PTGENDER, PTEDUCAT, SITE, AlzProg, CDRSB_bl, ADAS11_bl, ADAS13_bl,MMSE_bl, ABETA_bl, TAU_bl, PTAU_bl, AlzMCI_bl, conversion1year, conversion2year, conversion3year,conversion4year, conversion5year, conversion10year)
ADNI2 <- ADNI2 %>% select(PTID, Alz_bl, AGE, PTGENDER, PTEDUCAT, SITE, AlzProg, CDRSB_bl, MMSE_bl, ABETA_bl, TAU_bl, PTAU_bl, AlzMCI_bl, conversion1year, conversion2year, conversion3year,
conversion4year, conversion5year, conversion10year)
adnibis1 <- vroom(file = 'ADNI1_phenotypes_all.txt')
adnibis1 <- adnibis1 %>% select(PTID, ICV.y)
adnibis2 <- vroom(file = 'ADNI2_GO_phenotypes_all.txt')
adnibis2 <- adnibis2 %>% select(PTID, ICV.y)
adnibis <- rbind(adnibis1, adnibis2)
ADNI <- rbind(ADNI1, ADNI2)
ADNI <- merge(ADNI, adnibis, by.x = "PTID", by.y = "PTID")

# ADNI scores
adni <- read.table("SCORE_father_ADNI.profile", sep ="\t", header = T)
adni <- adni %>% select(IID, SCORE)
ADNI$PTID <- paste0(paste0(substr(ADNI$PTID, 1, 3), substr(ADNI$PTID, 5, 5)), substr(ADNI$PTID, 7, 10))
ADNI <- merge(ADNI, adni, by.x = "PTID", by.y = "IID")
```
#### Results
```{r eval=FALSE}
# Phenotype Alzheimer
# We also can test other phenotype by remplacing Alz_bl by conversion1year, Tau_bl, etc.
a <- glm(Alz_bl ~ SCORE + AGE + PTGENDER + ICV.y, data = ADNI, family = binomial())
a1 <- PseudoR2(a, which = "Efron")
b <- glm(Alz_bl ~ ICV.y + AGE + PTGENDER, data = ADNI, family = binomial())
b1 <- PseudoR2(b, which = "Efron")
b1-a1
summary(a)
```
### Father phenotype ADNI
```{r eval=FALSE}
# Parent
A1 <- vroom(file = 'ADNI1_parent.txt')
A1 <- A1 %>% select(PTID, FHQMOM, FHQDAD, FHQDADAD, FHQMOMAD,AGE, PTGENDER)
A2 <- vroom(file = 'ADNI2_parent')
A2 <- A2 %>% select(PTID, FHQMOM, FHQDAD, FHQDADAD, FHQMOMAD,AGE, PTGENDER)
A <- rbind(A1, A2)
adni <- read.table("SCORE_mother_ADNI.profile", sep ="\t", header = T)
adni <- adni %>% select(IID, SCORE)
A$PTID <- paste0(paste0(substr(A$PTID, 1, 3), substr(A$PTID, 5, 5)), substr(A$PTID, 7, 10))
A <- merge(A, adni, by.x = "PTID", by.y = "IID")
A <- merge(A, ADNI, by.x = "PTID", by.y = "PTID")
A <- A %>% filter(FHQDADAD == 0 | FHQDADAD == 1)
#Results
b <- glm(FHQDADAD ~ AGE.y + PTGENDER.y + ICV.y, data = A, family = binomial())
b1 <- PseudoR2(b, which = "Efron")
c <- glm(FHQDADAD ~ SCORE + AGE.y + PTGENDER.y + ICV.y, data = A, family = binomial())
c1 <- PseudoR2(c, which = "Efron")
c1-b1
summary(c)
```